---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# renumber

<!-- badges: start -->
<!-- badges: end -->

The goal of `renumber` is to make it easy to number or renumber files and directories. See Jenny Bryan's [presentation](http://www2.stat.duke.edu/~rcs46/lectures_2015/01-markdown-git/slides/naming-slides/naming-slides.pdf) on why you might want to do that. 

## Installation

You can install the released version of renumber from [gihub](https://github.com/richardjtelford/renumber) with:

``` r
install.packages("remotes")
remotes::install_github("richardjtelford/renumber")
```

## Example

To number files in the working directory, you could use this code.

```{r example, eval = FALSE}
library(renumber)
renumber(path = ".", number_dir = FALSE, test_only = TRUE)
```

Set `test_only` to FALSE for things to actually happen for real. 
Please be careful
